Figure 3b

### 2017-11-20 inst/coding_potential_cpc/coding_potential_cpc.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "Figure 1f"
subtitle: "miR34a asRNA coding potential via CPAT"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

####_Introduction_

We utilized a bioinformatic approach to evaluate the coding potential of the miR34a asRNA transcript. The Coding-potential assessment tool uses a linear regression model to evaluate coding-potential by examining ORF length, ORF coverage, Fickett score and hexamer score. We further confirmed these results using the Coding-potential Calculator which utilizes a support based machine-based classifier and accesses an alternate set of discriminatory features.

@@

####_Methods_

Protein-coding capacity was evaluated using the [Coding-potential Assessment Tool](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3616698/) and [Coding-potential Calculator](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1933232/) with default settings. Transcript sequences for use with Coding-potential Assessment Tool were downloaded from the UCSC genome browser using the following IDs: HOTAIR (ENST00000455246.1), XIST (ENST00000429829.1), β-actin (ENST00000331789.5), Tubulin (ENST00000427480.1), and MYC (ENST00000377970). Transcript sequences for use with Coding-potential Calculator were downloaded from the UCSC genome browser using the following IDs: HOTAIR (uc031qho.1), β-actin (uc003soq.4).

####_Results_

_Coding Potential Assesment Tool_

url <- "figure1f_codingPotentialCPAT/results.txt"
cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat

<div class = "caption">
Coding potential analysis results from the Coding-potential Assessment Tool including miR34a asRNA and two characterized non-coding transcripts (HOTAIR and XIST) and 3 known coding transcripts (β-actin, tubulin, and MYC). 
</div>

*Results for Coding-potential Calculator are located in Supplementary figure 1g.

####_Conclusions_

Results indicated that miR34a asRNA has a similar lack of coding capacity to the known non-coding transcripts HOTAIR and XIST and differs greatly when examining these parameters to the known coding transcripts beta-actin, tubulin, and MYC. However, to fully evaluate coding potential methods such as mass spectrometry or ribosome profiling must be used.

<br></br><br></br>

>>>>

---
title: "Supplementary Figure 1g"
subtitle: "miR34a asRNA coding potential via CPC"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

url <- "suppFigure1g_codingPotentialCPC/results.txt"
cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat

<div class = "caption">
Analysis of coding potential of the miR34a asRNA transcript using the Coding-potential Calculator including miR34a asRNA, the characterized non-coding transcript HOTAIR, and the known coding transcript β-actin. 
</div>

@@

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

pdf <- p + 
    geom_point(
    data = stats,
    aes(
      x = Treatment,
      y = mean,
      group = GOI
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    colour = "gray20"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Treatment,
      ymin = CI95l,
      ymax = CI95h,
      group = GOI
    ),
    colour = "gray20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = labelX,
      y = max + 0.3,
      label = pFormat,
      group = GOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.1,
      xend = xend,
      yend = max + 0.1,
      group = GOI
    ),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
  ))

>>>>

pdf <- p + 
    geom_point(
    data = stats,
    aes(
      x = Treatment,
      y = mean,
      group = GOI
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    colour = "gray20"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Treatment,
      ymin = CI95l,
      ymax = CI95h,
      group = GOI
    ),
    colour = "gray20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = labelX,
      y = max + 0.3,
      label = pFormat,
      group = GOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.1,
      xend = xend,
      yend = max + 0.1,
      group = GOI
    ),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
  ))

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

pdf <- p + 
  geom_point(
    data = stats,
    aes(x = Treatment, y = mean, group = Condition), 
    position = position_dodge(width = 0.9),
    colour = "gray20",
    shape = 95
  ) +
  geom_linerange(
    data = stats,
    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(x = Treatment, y = max + 0.28, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  )   +
  guides(
    fill = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 4)
    )
  )

>>>>

pdf <- p + 
  geom_point(
    data = stats,
    aes(x = Treatment, y = mean, group = Condition), 
    position = position_dodge(width = 0.9),
    colour = "gray20",
    shape = 95
  ) +
  geom_linerange(
    data = stats,
    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(x = Treatment, y = max + 0.28, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
    colour="grey43",
    size = 0.1,
    show.legend = FALSE
  )   +
  guides(
    fill = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 4)
    )
  )

### 2017-11-20 inst/isoforms/isoforms.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "miR34a asRNA isoforms"
author: "Jason T. Serviss"
date: "01/02/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We investigated the propensity of miR34a asRNA to be alternatively spliced, using PCR cloning and sequencing.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies), . All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was performed with the specified primer sets with annealing temperature 60˚C unless otherwise indicated. PCR was run for 35 cycles for those primer sets with annealing temperature 60˚C and 40 cycles in other cases. Resulting PCR products were run on a agarose gel, gel extracted with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced.

<br></br>
<center>![cloning gel](cloningGel.png)</center>
<br></br>
Cloned isoforms of the miR34a asRNA gene.

##Primers
```{r}
library(printr)
primers <- data.frame(
    name=c(
        "F12",
        "R1",
        "R2",
        "R3",
        "Ex3R1"
    ),
    sequence=c(
        "AAACACAAGCGTTTACCTGGGTGC",
        "TTGCCTCGTGAGTCCAAGGAGAAT",
        "ATAGGTTCATTTGCCCGATGTGCC",
        "CCACAGCTGTTGCTTCTGAATGCT",
        "TCAGATAGGTACCAAAAATGATGGCCGCAACTAATGACGGAT"
    )
)
primers
```

#Results

Product 8 resulted in miR34a AS 1  
Product 6 resulted in miR34a AS 2  
Product 2 resulted in miR34a AS 3  
Product 5 resulted in miR34a AS 4

<br></br>
<center>![isoforms.](isoforms.png)</center>
<br></br>
Cloned isoforms of the miR34a asRNA gene.

#Conclusions
Results indicate that the miR34a asRNA transcript is post-transcriptionally spliced to form several different isoforms.

>>>>

---
title: "Supplementary figure 1d"
subtitle: "miR34a asRNA isoform cloning"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We investigated the propensity of miR34a asRNA to be alternatively spliced, using PCR cloning and sequencing.

<br></br>

####_Methods_

<br></br>

_Cell culture and cloning_

All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies), . All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was performed with the specified primer sets with annealing temperature 60˚C unless otherwise indicated. PCR was run for 35 cycles for those primer sets with annealing temperature 60˚C and 40 cycles in other cases. Resulting PCR products were run on a agarose gel, gel extracted with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced. The sequencing results were visualized in the UCSC genome browser.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "F12",
        "R1",
        "R2",
        "R3",
        "Ex3R1"
    ),
    sequence=c(
        "AAACACAAGCGTTTACCTGGGTGC",
        "TTGCCTCGTGAGTCCAAGGAGAAT",
        "ATAGGTTCATTTGCCCGATGTGCC",
        "CCACAGCTGTTGCTTCTGAATGCT",
        "TCAGATAGGTACCAAAAATGATGGCCGCAACTAATGACGGAT"
    )
)
primers

```

<br></br>

####_Results_

```{r, out.width = "850px"}

url <- "suppFigure1d_isoforms/isoforms.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class = "caption">
Sequencing results from the analysis of miR34a asRNA isoforms in U2OS cells. miR34a AS ref. refers to the full length transcript as defined by the 3’-RACE and primer walk assay.
</div>

<br></br>

####_Conclusions_

Results indicate that the miR34a asRNA transcript is post-transcriptionally spliced to form several different isoforms.

<br></br><br></br>

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

```{r, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

@@

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2d_lnc34aCage.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(y = 1:length(pull(., level)))

@@

```{r, fig.align='center', fig.height=8, fig.width=12}
###plot

p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(2, "mm"),
    colour = "gray",
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(title = "RPKM", title.position = "top", title.hjust = 0.5))

p3 <- ggplot(data = NULL) + 
  geom_density(data = cage, aes(x = start)) +
  ggthemes::theme_few() +
  xlim(9241000, 9257900) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Density")

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
grid.newpage()
grid.draw(resize_heights(g, unit(c(3,1,1), "null")))
```

>>>>

```{r, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject",
    "ggthemes"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

@@

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2d_lnc34aCage.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(
      y = 1:length(pull(., level)),
      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
    )

@@

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
###plot rmarkdown

#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(2, "mm"),
    colour = "gray",
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(
    title = "RPKM", 
    title.position = "top", 
    title.hjust = 0.5)
  )

#density
p3 <- ggplot(data = NULL) + 
  geom_line(data = cage, aes(x = start), stat="density") +
  ggthemes::theme_few() +
  xlim(9241000, 9257900) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Density")

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
grid.newpage()
grid.draw(resize_heights(g, unit(c(3,1,1), "null")))

#plot pdf
#genes
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = grid::unit(1, "mm"),
    colour = "gray",
    lwd = 0.1
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 0.25
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE) +
  theme(
    axis.text = element_text(size = 3),
    axis.title.x = element_text(size = 4),
    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
    axis.ticks.length = unit(0.5, "mm"),
    axis.ticks = element_line(size = 0.15),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
  )

#cage
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(2, "pt"),
    colour = NA,
    lwd = 0.1,
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 4),
    legend.position = "top",
    legend.title = element_text(size = 4),
    legend.text = element_text(size = 4),
    legend.box.spacing = unit(3, "pt"),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
    strip.text.y = element_text(angle = 0)
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(
    title = "RPKM",
    title.position = "top",
    title.hjust = 0.5,
    barheight = unit(4, "pt"),
    barwidth = unit(40, "pt")
  ))

#density
p3 <- ggplot(data = NULL) + 
  geom_line(data = cage, aes(x = start), stat="density", lwd = 0.1) +
  ggthemes::theme_few() +
  xlim(9241000, 9257900) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size = 4),
    axis.ticks = element_blank(),
    panel.border = element_rect(fill = NA, size = 0.1),
    plot.margin = unit(c(0, 1, 0, 1), "mm")
  ) +
  labs(y = "Density")

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
g <- resize_heights(g, unit(c(6, 1, 1), "null"))
#grid.draw(g)

path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2d_lnc34aCage/suppFigure2d_lnc34aCage.pdf"
ggsave(
  plot = g, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

### 2017-11-20 inst/mir34a_locus/mir34a_locus.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "Figure 1b"
subtitle: "miR34a asRNA Expression Cell Panel"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

We wished to examine expression of miR34a asRNA in different cancer tissues and, therefore, utilized a panel of common cancer cell lines to detect miR34a asRNA expression, as well as, miR34a HG. We included both p53 wild type, p53 mutated, and p53 null cell lines in the cell line panel due to the fact that miR34a is a known downstream target of p53.

@@

_Cell culture and PCR_

Cells were cultured with the appropriate growth medium and seeded at a desity between 50-75% confluency. The following day, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was run for 35 or 38 or 16 cycles for miR34a asRNA, miR34a HG, and beta-actin, respectivley, with 58˚C annealing temperature. PCR products were analyzed on a 2% agarose gel.

_Primers_

primers <- data.frame(
    name=c(
        "miR34a asRNA F1",
        "miR34a asRNA R1",
        "miR34aHG_F",
        "miR34aHG_R",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers

@@

url <- "figure1b_miR34aASExpressionCellPanel/cellPanelLarge.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

<div class = "caption">
Semi-quantitative PCR data from the screening of a panel of cell lines. 
* Indicates that, although the cell line is p53wt, other mechanisms are present which inhibit p53 function. 
</div>

@@

####_Conclusions_

We were able to detect co-expression of both miR34a HG and miR34a AS in a variety of cell lines, including HCT116 human colon cancer cells and 293T human embryonic kidney cells.

>>>>

---
title: "Figure 1a"
subtitle: "miR34a Locus"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

An antisense transcript to the miR34a HG was detected using the UCSC genome browser.

@@

The USCS genome browser was utilized for the bioinformatic evaluation of antisense transcription at the miR34a locus.

@@

url <- "figure1a_miR34aLocus/miR34aLocus_hg38.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

<div class = "caption">
A schematic picture of the miR34a locus from the UCSC genome browser (hg38) including miR34a HG and mature miR34a, and LINC01759. H3K4me3 ChIP-seq and conservation over the locus is also shown.
</div>

@@

####_Conclusion_

GENCODE annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = construct,
      ymin = CI95l,
      ymax = CI95h,
      group = plotGene
    ),
    colour = "grey20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = construct,
      y = mean,
      group = plotGene
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    colour = "gray20",
    shape = 95
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.25, 
      label = pFormat, 
      group = gene
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(fill = guide_legend(
    title = "Gene", 
    override.aes = list(size = 4)
  ))

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = construct,
      ymin = CI95l,
      ymax = CI95h,
      group = plotGene
    ),
    colour = "grey20",
    size = 0.1,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = construct,
      y = mean,
      group = plotGene
    ),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    colour = "gray20",
    shape = 95
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.25, 
      label = pFormat, 
      group = gene
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(fill = guide_legend(
    title = "Gene", 
    override.aes = list(size = 4)
  ))

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.1
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.2,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  )

@@

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20",
    size = 0.1
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.2,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  )

@@

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 43,
 units = "mm"
)
```

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = phase, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = interaction(phase, condition)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey25",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = phase, 
      y = mean, 
      group = condition
    ), 
    colour = "black",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = stats,
    aes(
      x = x,
      y = y + 0.01, 
      xend = xend, 
      yend = y + 0.01
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = phase, 
      y = y + 0.025, 
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
  guides(
    fill = guide_legend(
      title = "Condition", 
      override.aes = list(size = 4)
    )
  )

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = phase, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = interaction(phase, condition)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey25",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = phase, 
      y = mean, 
      group = condition
    ), 
    colour = "black",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = stats,
    aes(
      x = x,
      y = y + 0.01, 
      xend = xend, 
      yend = y + 0.01
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = phase, 
      y = y + 0.025, 
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
  guides(
    fill = guide_legend(
      title = "Condition", 
      override.aes = list(size = 4)
    )
  )
